\Huge Conferences in the Era of Expensive Carbon

### 2019-06-25 main.tex
Nits

Beyond encouraging conferences to take these sorts of simple steps, public
accounting of conference emissions will generate data that future organizers
can use.  To this end, emissions data should be published both in aggregate
form (total and per-participant footprint), for quick reference, and in raw
form (a suitably anonymized record for each individual attending each
conference, including originating city), and it should be made available in
a central place and in a uniform format, to facilitate analysis.  (Most
conferences footprints will be dominated by participants' air travel, but the
data gathered should go beyond this to include air travel to in-person PC
meetings and estimated hotel and food {\COtwoE} footprints.)

ACM should provide tools for gathering and publicizing this data. As a
first step, SIGPLAN recently worked with ACM's SIG Governing Board to develop an
air-travel-focused {\COtwoE} calculator for conferences. Users can upload
conference registration data, and the calculator will estimate the {\COtwoE} cost
of air travel for those sufficiently far away. This calculator could be
expanded to account for other forms of conference emissions.

>>>>

Beyond encouraging conferences to take these sorts of simple steps, public
accounting of conference emissions will generate data that future organizers
can use.  To this end, emissions data should be published both in aggregate
form (total and per-participant footprint), for quick reference, and in raw
form (a suitably anonymized record for each individual attending each
conference, including originating city), and it should be made available in
a central place and in a uniform format, to facilitate analysis.  (Most
conferences' footprints will be dominated by participants' air travel, but the
data gathered should go beyond this to include air travel to in-person PC
meetings and estimated hotel and food {\COtwoE} footprints.)

ACM should provide tools to gather and publicize this data. As a
first step, SIGPLAN recently worked with ACM's SIG Governing Board to develop an
air-travel-focused {\COtwoE} calculator for conferences. Users can upload
conference registration data, and the calculator will estimate the {\COtwoE} cost
of air travel for those sufficiently far away. This calculator could be
expanded to account for other forms of conference emissions.
